% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Ethan Bogart}

\basicInfo{
  \email{ethan.bogart@yahoo.com} \textperiodcentered\ 
  \phone{(949)-468-9403} \textperiodcentered\
  \faGithub\ github.com/EthanBogart} 
  
 \smallskip

\textbf{Full stack developer} with experience writing production frontend code with React and Angular, and a passion for other languages and frameworks like Go and Ruby on Rails. I love building software that serves a purpose.

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Javascript, Go, Ruby, Python, Java
  \item Frameworks: React, Redux, Rails, Angular 1, Ionic, Gorilla Mux, Node, D3
  \item Databases: MySQL
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{HubSpot} Cambridge, MA}{June 2017 -- August 2017}
\role{Software Engineering Intern}\space
Frontend engineering in React and Redux
\begin{itemize}
  \item Rewrote user onboarding process to integrate with Redux
  \item Refactored and added unit tests for all actions
  \item Added a new message badge and a HubSpot branding option to the Messages product
\end{itemize}

\datedsubsection{\textbf{HomDNA} Newport Beach, CA}{May 2016 -- August 2016}
\role{Software Engineering Intern} \space
Hybrid mobile development with Node, Ionic and Angular 1
\begin{itemize}
  \item Greatly improved product searching experience with similarity checking
  \item Made many small improvements to overall UI, especially on Android
  \item Oversaw the entry of tens of thousands of home appliances to the product library 
\end{itemize}

\datedsubsection{\textbf{Tulane University} New Orleans, LA}{September 2015 -- May 2016}
\role{Teaching Assistant}\space
Grading and office hours for Introduction to Computer Science

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faWrench\ Projects}
\subsection{\textbf{Mr. Baseball Guy} Pebble Smartwatch App}
Displays live baseball scores and information using PebbleJS platform, and a Node backend to send notifications.
\begin{itemize}
  \item Store:\quad https://apps.getpebble.com/en\_US/application/57b17966f01b53ce0c000483?section=watchapps
\end{itemize}
\subsection{\textbf{Social Support System} Web Forum (In Development)}
Web forum for abused women, built with Ruby on Rails on top of the Thredded engine and a MySQL backend. Part of a class project working with other students.
\subsection{\textbf{Swarm Satellite Scheduler} Undergraduate Capstone Project (In Development)}
Project with a professor to help NASA implement and optimize a solution for a unique temporal constraint satisfaction problem (TCSP), to coordinate multiple missions on a swarm of small satellites. Written in Java. 
\subsection{\textbf{PolyWrite} Electron Desktop App (Defunct)}
User friendly document version control with UI. React/Redux/Electron frontend and a Go/MySQL backend.

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Tulane University}, New Orleans, Louisiana}{2014 -- Present}
\textit{Undergraduate} in Computer Science and Economics, Mathematics minor, expected graduation May 2018 \\
\textbf{3.77} GPA out of 4.0 in Computer Science

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
